---
author: "Chun Chieh(Jason) Chang, Bruhat Musunuru, Pan Fan"
title: "prepropyr-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{prepropyr-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(prepropyr)
```

# Introduction

The functions in `prepropyr` were developed to perform a quick EDA and data imputation and data scaling. Currently `nurser` contains three independent functions, this vignette outlines how to use these functions with toy data.

---

## `eda()` 

The eda() function helps to quickly explore the data by showing a pairplot and some summary statistics for a given dataframe .

```{r, message=FALSE}

df <- data.frame(num1 = c(8.5, 8, 9.2, 9.1, 9.4),
                  num2 = c(0.88, 0.93, 0.95 , 0.92 , 0.91),
                  num3 = c(0.46, 0.78, 0.66, 0.69, 0.52),
                  num4 = c(0.082, 0.078, 0.082, 0.085, 0.066),
                  cat1 = c("Good","Okay","Excellent","Terrible","Good"),
                  target = c(2,2,3,1,3))
```
After calling the eda() function, we can get following outputs,please see the docstring for more available outputs.

``` {r eda_result}
result <- eda(df,"target")
result$nb_num_features
```

``` {r eda_result2, out.width='80%'}
result$pairplot
```
---

## `imputation()`

The imputation() function will impute missing data in a tibble/dataframe given the chosen method(mean, median)

``` {r}
test_df <- data.frame('a' = c(1,NA,3), 'b' = c(5,6,NA), 'c' = c(NA,1,10))
test_df_imputed <- imputation(test_df, test_df, 'mean')
```

```{r impute_result}
test_df_imputed
```

---

## `scaler()`

This function scales numerical features based on scaling requirement(standardization, minmax Scaling) in a data.frame

```{r}
X_train <- data.frame('a' = c(1,2,3), 'b' = c(5,6,3), 'c' = c(2,1,10))
X_test <- data.frame('a' = c(1,5,3), 'b' = c(5,6,5), 'c' = c(2,5,10))
X_Valid <- data.frame('a' = c(5,5,3), 'b' = c(5,6,5), 'c' = c(2,5,10))
scaled_df <- scaler(X_train, X_Valid, X_test, scaler_type='standardization')
```

```{r scaler_result}
scaled_df
```

---
